Adaptive broadcast tree for multicores

### 2013-09-16 measurements/ziger_topologies.tex
Lot's of other things (including new results)

\begin{table}[htb]
  \centering
  \begin{tabular}{lrrrrr}
  \toprule
  & \multicolumn{3}{c}{Real hardware [cycles]} & \multicolumn{2}{c}{Simulation [units]} \\
  topology & time & factor & stderr & time & factor \\
  \midrule
  cluster & 2634.91 & 1.017 & 48.11 & 334 & 1.100 \\
  mst & 3178.59 & 1.227 & 43.28 & 343 & 1.129 \\
  bintree & 3380.46 & 1.305 & 42.70 & 377 & 1.242 \\
  sequential & 3841.91 & 1.483 & 239.48 & 672 & 2.214 \\
  badtree & 5711.52 & 2.204 & 30.49 & 714 & 2.354 \\
  adaptivetree & 2591.14 & \colorbox{gray}{1.000} & 45.12 & 303 & \colorbox{gray}{1.000} \\
  \midrule
  \end{tabular}
  \caption{Topology evaluation for \ziger}
  \label{tab:ziger}
\end{table}

>>>>

\begin{figure}
  \caption{topology results for \ziger}
  \label{pgfplot:20130905}
  \begin{tikzpicture}[scale=1]
    \begin{axis}[ybar,ymin=0,symbolic x coords={cluster,mst,bintree,badtree,adaptivetree},xtick=data,error bars/y dir=both,error bars/y explicit,legend style={ at={(0.5,1.03)}, anchor=south },legend columns=2,xlabel={topology},ylabel={cost [cycles]}]
    \addplot coordinates {
      (cluster,     3674.399889) +- (182.956438,182.956438)
      (mst,         3752.560889) +- (242.747418,242.747418)
      (bintree,     3776.717889) +- (277.739474,277.739474)
      (badtree,     5311.408333) +- ( 72.719583, 72.719583)
      (adaptivetree,3202.816778) +- (270.823914,270.823914)
    };
    \addplot coordinates {
      (cluster,     3546.492553)
      (mst,         3477.927649)
      (bintree,     3849.849689)
      (badtree,     6171.924742)
      (adaptivetree,3202.816778)
    };
    \legend{real hardware, simulation};
    \end{axis}
  \end{tikzpicture}
\end{figure}
